### 2016-07-21 paper/paper.tex
minor typos, +acknowledgements section

\noindent\textbf{Contributions:}
\begin{itemize}
\item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
incentives miners to participate in a DDoS attack, and allows them prove they have done so
\item Describe a way for target victims to be chosen by consensus of its
participants
\item Implement our proof-of-work function and evaluate its performance and
impact
\item Discuss several defenses against such a cryptocurrency that potential
victims can employ
\end{itemize}

@@

Permacoin is a proposed altcoin that uses a novel
\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
resources solving a useless proof-of-work puzzle, such as in Bitcoin, miners are
instead incentivized to store parts of a large agreed-upon file. In order to be
competitive in Permacoin, miners prove that they can retrieve an assigned
portion of the file.

@@

Peercoin's proof-of-stake allows currency holders to mint new blocks based on
how many coin-days they are able and willing to consume. ``Coin-days consumed''
is a measure of the product of the amount of coins spent in a transaction, and
the number of days since they were last spent. For example, to consume 10
coin-days, a currency holder can spend 10 Peercoin that they have held for a
day, or equivalently, spend 5 Peercoins that were last spent 2 days ago. Note
that the holder can send these coins to anyone, including themselves, in order
to consume the coin age.

@@

If the SHA256 hash of the server key exchange parameters, signature, and
miner-chosen nonce $N$ is less than the current target difficulty, then this
connection satisfies the proof-of-work threshold, and can be used to form the
next block. We hash $N$ a second time in this way to prevent the victim server
from being able to tell if their response would satisfy the target difficulty.
Otherwise, servers could simply withhold such responses, and no blocks could be
published for them.

@@

>>>>

\noindent\textbf{Contributions:}
\begin{itemize}
\item Propose a novel conceptual cryptocurrency, DDoSCoin, whose proof-of-work
incentives miners to participate in a DDoS attack, and allows them to prove they have done so
\item Describe a way for target victims to be chosen by consensus of its
participants
\item Implement our proof-of-work function and evaluate its performance and
impact
\item Discuss several defenses against such a cryptocurrency that potential
victims can employ
\end{itemize}

@@

Permacoin is a proposed altcoin that uses a novel
\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
resources solving a useless proof-of-work puzzle (such as in Bitcoin), miners are
instead incentivized to store parts of a large agreed-upon file. In order to be
competitive in Permacoin, miners prove that they can retrieve an assigned
portion of the file.

@@

Peercoin's proof-of-stake allows currency holders to mint new blocks based on
how many coin-days they are able and willing to consume. ``Coin-days consumed''
is a measure of the product of the amount of coins spent in a transaction, and
the number of days since they were last spent. For example, to consume 10
coin-days, a currency holder can spend 10 Peercoin that they have held for a
day, or equivalently, spend 5 Peercoins that were last spent 2 days ago. Note
that the holder can send these coins to anyone---including themselves---in order
to consume the coin age.

@@

If the SHA256 hash of the server key exchange parameters, signature, and
miner-chosen nonce $N$ is less than the current target difficulty, then this
connection satisfies the proof-of-work threshold, and can be used to form the
next block. We hash $N$ a second time in this way to prevent the victim server
from being able to tell if their response would satisfy the target difficulty.
Otherwise, servers could simply withhold such infrequent responses, and no blocks could be
published for them.

@@

\section*{Acknowledgements}

The authors are grateful for the support and various discussions on DDoSCoin. We
thank David Adrian, Matt Bernhard, and Drew Springall for their discussions
concerning the feasibility of the proof-of-DDoS idea. We also thank the
anonymous reviewers for their helpful feedback.
